---
title: "Home"
output:
  html_document:
    toc: false
---

This website demonstrates the current basic functionality of workflowr to
archive objects and restore them for later comparison.

The analysis [archive.html](archive.html) simulates some data from a normal 
distribution based on a randomly chosen mean value. Each time it is committed 
and built, new archive files are created with `wflow_archive`. These are then 
restored for comparison with `wflow_restore`. The archive files are saved in 
`archive/archive.Rmd/`.

This is an early prototype with many decisions still to be made. See the section
[Decisions](archive.html#decisions).

To install this version of [workflowr](https://github.com/jdblischak/workflowr)
for testing, install from the branch
[feature_archive](https://github.com/jdblischak/workflowr/tree/feature_archive):

```{r feature-archive, eval=FALSE}
devtools::install_github("jdblischak/workflowr@feature_archive",
                         build_vignettes = TRUE)
```

To return to the latest stable version of workflowr after testing, run the
following:

```{r stable, eval=FALSE}
devtools::install_github("jdblischak/workflowr",
                         build_vignettes = TRUE)
```
